Staged Abstract Interpreters

### 2019-09-10 paper/60_cases.tex
title and subsection titles
typo
polish

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Control-flow Analysis} \label{cfa}

@@

\subsubsection{Context-sensitivity}

@@

\subsubsection{Store-widened Analysis}

@@

The skeleton of a staged version of abstract garbage collection implementation
is shown in Figure \ref{fixgc}.
We refactor the @fix@ function with caching (from Section \ref{sai}) to @fix_gc@
(the caching part is omitted in the presented code snippet). Several auxiliary
functions are used: @ask_root@ retrieves the current root addresses from the
monad stack; @root@ computes the reachable addresses given a value; and @gc@
performs garbage collection according to the given reachable addresses and
returns a new store. For the generic interpreter, we also need to compute the
root addresses for compound expressions; for the detail of this part, readers
may refer to \cite{DBLP:journals/pacmpl/DaraisLNH17}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Control-Flow Analysis} \label{cfa}

@@

\subsubsection{Context-Sensitivity}

@@

\subsubsection{Store-Widened Analysis}

@@

The skeleton of a staged version of abstract garbage collection implementation
is shown in Figure \ref{fixgc}.
We refactor the @fix@ function with caching (used in Section \ref{sai}) to @fix_gc@
(the caching part is omitted in the presented code snippet). Several auxiliary
functions are used: @ask_root@ retrieves the current root addresses from the
monad stack; @root@ computes the reachable addresses given a value; and @gc@
performs garbage collection according to the given reachable addresses and
returns a new store. We also need to compute the root addresses for compound
expressions, which is elided in the code snippet; for the details of this part,
readers may refer to \cite{DBLP:journals/pacmpl/DaraisLNH17}.
